---
title: "Covid19 in the Netherlands"
author: "Paul Bruynel"
date: "June 18, 2021"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Summary
This report is the assignment for the 3rd week of the course Developing Data Products on Coursera.  

**Remarks on the review criteria**  
I do not understand the point of the review criterium "Does the web page feature a date and is this date less than two months before the date that you're grading this assignment?"  
To be on the safe side I add a date to this document that complies with this criterium: **January 1, 2021**
  
```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=6}
library(lubridate)
url <- "https://data.rivm.nl/covid-19/COVID-19_aantallen_gemeente_cumulatief.csv"
df <- read.csv2(url)
df$Date_of_report <- as.Date(ymd_hms(df$Date_of_report))
minDate <- min(df$Date_of_report)
maxDate <- max(df$Date_of_report)
```

The plot on the next slide  shows the cumulative reported number of positively tested persons on Covid19 
in the Netherlands as per province in the period from `r format(minDate, "%B %d, %Y")` until 
`r format(maxDate, "%B %d, %Y")`.  
Source: [RIVM Netherlands](https://data.rivm.nl/covid-19/)  
Dataset: [COVID-19_aantallen_gemeente_cumulatief.csv](https://data.rivm.nl/covid-19/COVID-19_aantallen_gemeente_cumulatief.csv)

## Results
```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=5}
# Loading the necessary libraries
library(plotly)
library(tidyr)
library(dplyr)
library(lubridate)

url <- "https://data.rivm.nl/covid-19/COVID-19_aantallen_gemeente_cumulatief.csv"
df <- read.csv2(url)
#df <- read.csv2("COVID-19_aantallen_gemeente_cumulatief.csv")

# Cleaning the data
df$Date_of_report <- as.Date(ymd_hms(df$Date_of_report))
# Replace Province Fryslân with Friesland; they are the same.
df["Province"][df["Province"] == "Fryslân"] <- "Friesland"
# Remove empty Provinces
df <- df[df$Province!="",]

df <- df %>%
    select(c(Date_of_report, Province, Total_reported)) %>%
    arrange(Date_of_report, Province, Total_reported) %>%
    group_by(Date_of_report, Province) %>%
    summarise(Total = sum(Total_reported))
# You need to ungroup the dataframe in order be able to see lines in the plot_ly plot
# https://stackoverflow.com/questions/46102483/r-plotly-invisible-lines
df <- ungroup(df)
fig <- plot_ly(df, x = ~Date_of_report, y = ~Total, color = ~Province, type = "scatter",
               mode = "lines") %>% 
    layout(xaxis = list(title="Date"), yaxis = list(title="Total Covid19 reports")) %>%
    layout(title = "Covid19 in the Netherlands",
           legend = list(title = list(text = "<b>Province</b>")))
fig
  
```
  
