---
title: "MyPlotly"
author: "Paul Bruynel"
date: "6/10/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Basic Scatterplot
A basic scatterplot is easy to make, with the added benefit of tooltips that
appear when your mouse hovers over each point. Specify a scatterplot by
indicating `type = "scatter"`. Notice that the arguments for the `x` and `y` 
variables as specified as formulas, with the tilde operator (`~`) preceding the
variable that you're plotting.  
This is a scatterplot for the iris dataset:
```{r, echo=FALSE, message=FALSE, warning=FALSE}
library(plotly)
data("iris")
plot_ly(iris, x = ~Petal.Width, y = ~Petal.Length, type = "scatter")
```

## Added color
```{r, echo=FALSE, message=FALSE, warning=FALSE}
plot_ly(iris, x = ~Petal.Width, y = ~Petal.Length, type = "scatter", color = ~Species, size = ~Sepal.Length)
plot_ly(iris, x = ~Sepal.Width, y = ~Sepal.Length, type = "scatter", color = ~Species, size = ~Petal.Length)
```

## 3D scatterplot
```{r, echo=FALSE, message=FALSE, warning=FALSE}
plot_ly(iris, x = ~Sepal.Length, y = ~Petal.Width, z = ~Petal.Length, type = "scatter3d", color = ~Species, size = ~Sepal.Width)
```

## Stockmarket
Lineplots
```{r, echo=FALSE, message=FALSE, warning=FALSE}
library(plotly)
library(tidyr)
library(dplyr)
data("EuStockMarkets")

stocks <- as.data.frame(EuStockMarkets) %>%
  gather(index, price) %>%
  mutate(time = rep(time(EuStockMarkets), 4))

plot_ly(stocks, x = ~time, y = ~price, color = ~index, type = "scatter", mode = "lines")
```

```{r, echo=FALSE, message=FALSE, warning=FALSE}
library(plotly)
library(tidyr)
library(dplyr)
df <- read.csv2("COVID-19_aantallen_gemeente_cumulatief.csv")

library(lubridate)
df$Date_of_report <- as.Date(ymd_hms(df$Date_of_report))
df$Province <- as.factor(df$Province)

df <- df %>%
    select(c(Date_of_report, Province, Total_reported)) %>%
    arrange(Date_of_report, Province, Total_reported)
df <- df %>%
    group_by(Date_of_report, Province) %>%
    summarise(Total = sum(Total_reported))

plot_ly(df, x = ~Date_of_report, y = ~Total, color = ~Province, type = "scatter", mode = "lines")
# df3 <- df[df$Province %in% c('Drenthe', 'Flevoland', 'Friesland', 'Gelderland', 'Groningen',                               'Limburg', 'Noord-Brabant', 'Noord-Holland', 'Overijssel') ,]
df3 <- df[df$Province %in% c('Drenthe', 'Flevoland') ,]
plot_ly(df3, x = ~Date_of_report, y = ~Total, color = ~Province, type = "scatter", mode = "lines")

```


## Histogram
```{r, echo=FALSE, message=FALSE, warning=FALSE}
plot_ly(iris, x = ~Sepal.Width, type = "histogram")
```

## Boxplot
```{r, echo=FALSE, message=FALSE, warning=FALSE}
plot_ly(iris, y = ~Petal.Length, type = "box", color = ~Species)
```

## Heatmap 2D
```{r, echo=FALSE, message=FALSE, warning=FALSE}
terrain1 <- matrix(rnorm(100*100), nrow=100, ncol=100)
plot_ly(z = terrain1, type = "heatmap")
```

## Heatmap 3D (Surface)
```{r, echo=FALSE, message=FALSE, warning=FALSE}
terrain2 <- matrix(sort(rnorm(100*100)), nrow=100, ncol=100)
plot_ly(z = terrain2, type = "surface")
```

## Choropleth Maps

```{r, echo=FALSE, message=FALSE, warning=FALSE}
# Create data frame
state_pop <- data.frame(State = state.abb, Pop = as.vector(state.x77[,1]))
# Create hover text
state_pop$hover <- with(state_pop, paste(State, '<br>', "Population:", Pop))
# Make state borders white
borders <- list(color = toRGB("red"))
# Set up some mapping options
map_options <- list(
  scope = 'usa',
  projection = list(type = 'albers usa'),
  showlakes = TRUE,
  lakecolor = toRGB('white')
)

plot_ly(z = ~state_pop$Pop, text = ~state_pop$hover, locations = ~state_pop$State, 
        type = 'choropleth', locationmode = 'USA-states', 
        color = state_pop$Pop, colors = 'Blues', marker = list(line = borders)) %>%
  layout(title = 'US Population in 1975', geo = map_options)
```

## Make ggplot plots interactive - convert ggplot to plot_ly
```{r, echo=FALSE, message=FALSE, warning=FALSE}
library(ggplot2)
set.seed(100)
d <- diamonds[sample(nrow(diamonds), 1000), ]

p <- ggplot(data=d, aes(x=carat, y=price)) +
  geom_point(aes(text=paste("Clarity:", clarity)), size=4) +
  geom_smooth(aes(color=cut, fill=cut)) + facet_wrap(~cut)

(gg <- ggplotly(p))

```
